---
title: "Asean Meat Production 2018 - 2021"
author: "Team Peru"
format: html
toc: true
number-sections: true
---

```{r}
#| label: setup-meat
#| message: false
library(tidyverse)
meat <- read_csv("meat.csv")
```

# Inspect the `meat` Tibble

## Prediction Individual

### Predict Class
country: Character\
animal: Character\
year: Numeric\
production: Numeric

### Predict Number of Distinct Values
country: 10\
animal: 7\
year: 4

### Predict the Values
nrow(meat) = 280\
ncol(meat) = 4

## Answer by Querying

### Class

#### Country
```{r}
#| label: meat-class-country
#| echo: true
#| eval: true
#| include: true
class(meat$country)
```

#### animal
```{r}
#| label: meat-class-animal
#| echo: true
#| eval: true
#| include: true
class(meat$animal)
```

#### year
```{r}
#| label: meat-class-year
#| echo: true
#| eval: true
#| include: true
class(meat$year)
```

#### production
```{r}
#| label: meat-class-production
#| echo: true
#| eval: true
#| include: true
class(meat$production)
```

### Distinct Values

#### country
```{r}
#| label: distinct-values
#| echo: true
#| eval: true
#| include: true
length(unique(meat$country))
```
#### animal
```{r}
#| label: distinct-values-animal
#| echo: true
#| eval: true
#| include: true
length(unique(meat$animal))
```
#### year
```{r}
#| label: distinct-values-year
#| echo: true
#| eval: true
#| include: true
length(unique(meat$year))
```

### Number of Rows and Columns

#### Number of Rows of Meat
```{r}
#| label: nrow-meat
#| echo: true
#| eval: true
#| include: true
nrow(meat)
```
#### Number of Columns of Meat
```{r}
#| label: ncol-meat
#| echo: true
#| eval: true
#| include: true
ncol(meat)
```

### Cross Check Through glimpse()
```{r}
#| label: cross-check-glimpse
#| echo: true
#| eval: true
#| include: true
glimpse(meat)
```

## Looking Into The Rows

### Head
```{r}
#| label: head-meat
#| echo: true
#| eval: true
#| include: true
head(meat)
```

### Tail
```{r}
#| label: tail-meat
#| echo: true
#| eval: true
#| include: true
tail(meat)
```

# Handle Missing Values

## Checking if There Are Missing Values
```{r}
#| label: if-there-is-missing-values
#| echo: true
#| eval: true
#| include: true
any(is.na(meat$production))
```

## List production Column That Is NA
```{r}
#| label: list-missing-values
#| echo: true
#| eval: true
#| include: true
meat[is.na(meat$production), c("country", "animal", "year")]
```

### Cross Check Mising Rows By Second Method
```{r}
#| label: cross-check-missing-rows
#| echo: true
#| eval: true
#| include: true
expected_decrease <- sum(is.na(meat$production))
meat_complete <- meat[!is.na(meat$production), ]
actual_decrease <- nrow(meat) - nrow(meat_complete)
actual_decrease == expected_decrease
```

## Compute Total ASEAN Production Across All Years

### Without NA Data Removed
```{r}
#| label: total-production-without-na
#| echo: true
#| eval: true
#| include: true
sum(meat$production)
```

### With NA Data Removed
```{r}
#| label: total-production-with-na
#| echo: true
#| eval: true
#| include: true
sum(meat$production, na.rm = TRUE)
```

## Assumptions And Whether That Assumption Is Justifiable (TODO)

# Compare Countries in 2020

## Country With The Maximum Poultry Production In 2020
```{r}
#| label: country-with-maximum-poultry-production-2020
#| echo: true
#| eval: true
#| include: true
mask_2020_poultry <- meat$year == 2020 & meat$animal == "poultry"
poultry_2020 <- meat[mask_2020_poultry, ]
max_prod_2020 <- max(poultry_2020$production, na.rm = TRUE)
poultry_2020$country[poultry_2020$production == max_prod_2020]
```

### Cross Check By Second Method
```{r}
#| label: cross-check-max-poultry-2020
#| echo: true
#| eval: true
#| include: true
max_val <- max(poultry_2020$production, na.rm = TRUE)
top_country_v1 <- poultry_2020$country[poultry_2020$production == max_val]
poultry_2020$rank_desc <- min_rank(desc(poultry_2020$production))
top_country_v2 <- poultry_2020$country[poultry_2020$rank_desc == 1]
identical(top_country_v1, top_country_v2)
```

## Country With Second-Highest Poultry Production In 2020
```{r}
#| label: country-with-second-highest-poultry-production-2020
#| echo: true
#| eval: true
#| include: true
poultry_2020 <- meat[meat$year == 2020 & meat$animal == "poultry", ]
poultry_2020$prod_rank <- min_rank(desc(poultry_2020$production))
poultry_2020$country[poultry_2020$prod_rank == 2]
```

## Country With More Poultry Than Pig Produced In 2020
```{r}
#| label: country-with-more-poultry-than-pig-2020
#| echo: true
#| eval: true
#| include: true
poultry_2020 <- meat[meat$year == 2020 & meat$animal == "poultry", ]
pig_2020 <- meat[meat$year == 2020 & meat$animal == "pig", ]
identical(poultry_2020$country, pig_2020$country)
sum(poultry_2020$production > pig_2020$production, na.rm = TRUE)
```

# Construct Factors

## Convert animal To Factor And Assign Result To New Column animal_factor With Confirmation
```{r}
#| label: construct-factors
#| echo: true
#| eval: true
#| include: true
meat$animal_factor <- factor(meat$animal)
is.factor(meat$animal_factor)
```

## Report Results Of animal_factor

### Report Levels Of New Factor Column
```{r}
#| label: report-levels
#| echo: true
#| eval: true
#| include: true
levels(meat$animal_factor)
```

### Check If Ordered Alphabetically
```{r}
#| label: check-order
#| echo: true
#| eval: true
#| include: true
identical(
  min_rank(levels(meat$animal_factor)),
  1:length(levels(meat$animal_factor))
)
```

## Should meat$animal_factor Be An Ordered Factor?

## Color Factor With Confirmation
```{r}
#| label: colour-factor
#| echo: true
#| eval: true
#| include: true
meat$color <- fct_collapse(
  meat$animal_factor,
  red = c("beef and buffalo", "mutton and goat", "pig"),
  white = "poultry"
)

levels(meat$color)
```

# Add Country-Code Column
```{r}
#| label: add-country-code
#| echo: true
#| eval: true
#| include: true
meat$iso3 <- recode_values(
  meat$country,
  "Brunei Darussalam" ~ "BRN",
  "Cambodia" ~ "KHM",
  "Indonesia" ~ "IDN",
  "Lao PDR" ~ "LAO",
  "Malaysia" ~ "MYS",
  "Myanmar" ~ "MMR",
  "Philippines" ~ "PHL",
  "Singapore" ~ "SGP",
  "Thailand" ~ "THA",
  "Viet Nam" ~ "VNM"
)
any(is.na(meat$iso3))
nrow(unique(meat[, c("country", "iso3")]))
```