---
title: "Asean Meat Production 2018 - 2021"
author: "Team Peru"
format: html
toc: true
number-sections: true
---

```{r}
#| label: setup-meat
#| message: false
library(tidyverse)
meat <- read_csv("meat.csv")
```

# Inspect the `meat` Tibble

## Prediction Individual

## Travis' Predicition
a.
country: character
animal: character
year: numeric
production: numeric

b.
country: 10
animal: 7
year: 4

c.
nrow(meat): 280
ncol(meat): 4

## Jie Yung Predicition 

a.
Country: Character
Animal: Character
Year: Numeric
Production: Numeric

b.
country: 10
animal: 6
year: 4

c. 
nrow(meat): 100
ncol(meat): 6

## Wee Han Predicition 

a.
Country: Character
Animal: Character
Year: Numeric
Production: Numeric

b.
country: 10
animal: 8
year: 4

c. 
nrow(meat): 280
ncol(meat): 4

### Predict Class
country: Character\
animal: Character\
year: Numeric\
production: Numeric

### Predict Number of Distinct Values
country: 10\
animal: 7\
year: 4

### Predict the Values
nrow(meat) = 280\
ncol(meat) = 4

## Answer by Querying

### Class

#### Country
```{r}
#| label: meat-class-country
#| echo: true
#| eval: true
#| include: true
class(meat$country)
```

#### animal
```{r}
#| label: meat-class-animal
#| echo: true
#| eval: true
#| include: true
class(meat$animal)
```

#### year
```{r}
#| label: meat-class-year
#| echo: true
#| eval: true
#| include: true
class(meat$year)
```

#### production
```{r}
#| label: meat-class-production
#| echo: true
#| eval: true
#| include: true
class(meat$production)
```

### Distinct Values

#### country
```{r}
#| label: distinct-values
#| echo: true
#| eval: true
#| include: true
length(unique(meat$country))
```

#### animal
```{r}
#| label: distinct-values-animal
#| echo: true
#| eval: true
#| include: true
length(unique(meat$animal))
```

#### year
```{r}
#| label: distinct-values-year
#| echo: true
#| eval: true
#| include: true
length(unique(meat$year))
```

### Number of Rows and Columns

#### Number of Rows of Meat
```{r}
#| label: nrow-meat
#| echo: true
#| eval: true
#| include: true
nrow(meat)
```

#### Number of Columns of Meat
```{r}
#| label: ncol-meat
#| echo: true
#| eval: true
#| include: true
ncol(meat)
```

### Cross Check Through glimpse()
```{r}
#| label: cross-check-glimpse
#| echo: true
#| eval: true
#| include: true
glimpse(meat)
```

## Looking Into The Rows

### Head
```{r}
#| label: head-meat
#| echo: true
#| eval: true
#| include: true
head(meat)
```

### Tail
```{r}
#| label: tail-meat
#| echo: true
#| eval: true
#| include: true
tail(meat)
```

### Observations and surprises

Year runs backwards. The data opens at 2021 and closes at 2018 — most people would expect chronological order (oldest first), but it's newest-first. 

Countries are alphabetical within each group. Brunei → Cambodia → Indonesia → Lao PDR → Malaysia → Myanmar in the head; Malaysia → Myanmar → Philippines → Singapore → Thailand → Viet Nam in the tail. 

"Viet Nam" is two words. It appears as "Viet Nam" rather than the more commonly typed "Vietnam", which could cause a mismatch if you ever join this dataset against another source.

# Handle Missing Values

## Checking if There Are Missing Values
```{r}
#| label: if-there-is-missing-values
#| echo: true
#| eval: true
#| include: true
any(is.na(meat$production))
```

## List production Column That Is NA
```{r}
#| label: list-missing-values
#| echo: true
#| eval: true
#| include: true
meat[is.na(meat$production), c("country", "animal", "year")]
```


### Cross Check Missing Rows By Second Method
```{r}
#| label: cross-check-missing-rows
#| echo: true
#| eval: true
#| include: true
expected_decrease <- sum(is.na(meat$production))
meat_complete <- meat[!is.na(meat$production), ]
actual_decrease <- nrow(meat) - nrow(meat_complete)
actual_decrease == expected_decrease
```

```{r}
#| label: verify-missing-production
nrow(meat)
nrow(meat[!is.na(meat$production), ])
nrow(meat) - nrow(meat[!is.na(meat$production), ])
```

## Compute Total ASEAN Production Across All Years

### Without NA Data Removed
```{r}
#| label: total-production-without-na
#| echo: true
#| eval: true
#| include: true
sum(meat$production)
```

### With NA Data Removed
```{r}
#| label: total-production-with-na
#| echo: true
#| eval: true
#| include: true
sum(meat$production, na.rm = TRUE)
```

### Summary of missing production values and total production

The code confirms that the `production` column contains missing values because `any(is.na(meat$production))` returns `TRUE`. We then used the logical mask `is.na(meat$production)` to filter the dataset and display only the rows where production is missing. The missing rows are shown using only the `country`, `animal`, and `year` columns so that we can clearly identify where the missing production values occur.

To cross-check the number of missing rows, we calculated the expected decrease in rows by summing the number of `NA` values in the `production` column. We then created a new dataset called `meat_complete` that excludes rows with missing production values. By comparing the actual decrease in rows with the expected decrease, we confirmed that they match. This validates our identification of the missing values. The row count decreases from 160 to 156, confirming that there are 4 missing production values in the dataset.

For the total production calculation, `sum(meat$production)` returns `NA` because the `production` column still contains missing values. R does not know how to add an unknown value, so the whole result becomes `NA`. When we use `sum(meat$production, na.rm = TRUE)`, R ignores the 4 missing values and adds up the remaining 156 known production values. This returns `83,937.52`, which represents the total ASEAN meat production from the non-missing records.

### Assumption made by using `na.rm = TRUE`

Using `na.rm = TRUE` assumes that it is acceptable to ignore the missing production values instead of estimating or replacing them. This means the missing rows do not contribute to the total production calculation.

This assumption is acceptable for a simple exploratory calculation because only 4 out of 160 production values are missing. However, it is not perfect because those missing rows still represent real country-animal-year records. If the missing production values were large, ignoring them would underestimate the true total ASEAN meat production.

# Compare Countries in 2020

## Country With The Maximum Poultry Production In 2020
```{r}
#| label: country-with-maximum-poultry-production-2020
#| echo: true
#| eval: true
#| include: true
mask_2020_poultry <- meat$year == 2020 & meat$animal == "poultry"
poultry_2020 <- meat[mask_2020_poultry, ]
max_prod_2020 <- max(poultry_2020$production, na.rm = TRUE)
poultry_2020$country[poultry_2020$production == max_prod_2020]
```

### Cross Check By Second Method
```{r}
#| label: cross-check-max-poultry-2020
#| echo: true
#| eval: true
#| include: true
max_val <- max(poultry_2020$production, na.rm = TRUE)
top_country_v1 <- poultry_2020$country[poultry_2020$production == max_val]
poultry_2020$rank_desc <- min_rank(desc(poultry_2020$production))
top_country_v2 <- poultry_2020$country[poultry_2020$rank_desc == 1]
identical(top_country_v1, top_country_v2)
```

## Country With Second-Highest Poultry Production In 2020
```{r}
#| label: country-with-second-highest-poultry-production-2020
#| echo: true
#| eval: true
#| include: true
poultry_2020 <- meat[meat$year == 2020 & meat$animal == "poultry", ]
poultry_2020$prod_rank <- min_rank(desc(poultry_2020$production))
poultry_2020$country[poultry_2020$prod_rank == 2]
```

## Country With More Poultry Than Pig Produced In 2020
```{r}
#| label: country-with-more-poultry-than-pig-2020
#| echo: true
#| eval: true
#| include: true
poultry_2020 <- meat[meat$year == 2020 & meat$animal == "poultry", ]
pig_2020 <- meat[meat$year == 2020 & meat$animal == "pig", ]
identical(poultry_2020$country, pig_2020$country)
sum(poultry_2020$production > pig_2020$production, na.rm = TRUE)
```

### Summary of 2020 country comparison

The results show that Indonesia had the highest poultry production in 2020, while Thailand had the second highest poultry production in 2020. The comparison between poultry and pig production also shows that 6 countries produced more poultry than pig in 2020.

The `identical()` check is important because it confirms that the country order in the poultry and pig vectors is the same before comparing their production values. This means each poultry value is being compared with the pig value for the same country.

# Construct Factors

## Convert animal To Factor And Assign Result To New Column animal_factor With Confirmation
```{r}
#| label: construct-factors
#| echo: true
#| eval: true
#| include: true
meat$animal_factor <- factor(meat$animal)
is.factor(meat$animal_factor)
```

## Report Results Of animal_factor

### Report Levels Of New Factor Column
```{r}
#| label: report-levels
#| echo: true
#| eval: true
#| include: true
levels(meat$animal_factor)
```

### Check If Ordered Alphabetically
```{r}
#| label: check-order
#| echo: true
#| eval: true
#| include: true
identical(
  min_rank(levels(meat$animal_factor)),
  1:length(levels(meat$animal_factor))
)
```

## Should meat$animal_factor Be An Ordered Factor?

The output of `levels(meat$animal_factor)` shows that the animal factor has four levels: `beef and buffalo`, `mutton and goat`, `pig`, and `poultry`. The alphabetical check returns `TRUE`, which means the levels are arranged alphabetically.

`meat$animal_factor` should not be an ordered factor because the animal categories do not have a natural ranking. For example, `beef and buffalo`, `mutton and goat`, `pig`, and `poultry` are different categories of meat, but one is not naturally higher or lower than another. An ordered factor would be more suitable for categories such as `low`, `medium`, and `high`, where the order has meaning. Therefore, it is appropriate for `meat$animal_factor` to be an unordered factor.

## Color Factor With Confirmation
```{r}
#| label: colour-factor
#| echo: true
#| eval: true
#| include: true
meat$color <- fct_collapse(
  meat$animal_factor,
  red = c("beef and buffalo", "mutton and goat", "pig"),
  white = "poultry"
)

levels(meat$color)
```

The `fct_collapse()` function groups the original animal categories into broader meat-colour categories. `beef and buffalo`, `mutton and goat`, and `pig` are collapsed into the `red` level, while `poultry` is collapsed into the `white` level. The output of `levels(meat$color)` confirms that the new factor has two levels: `red` and `white`. This indicates that the collapse was successful, and the new `color` factor correctly categorizes the meats into red and white groups.


# Add Country-Code Column
```{r}
#| label: add-country-code
#| echo: true
#| eval: true
#| include: true
meat$iso3 <- recode_values(
  meat$country,
  "Brunei Darussalam" ~ "BRN",
  "Cambodia" ~ "KHM",
  "Indonesia" ~ "IDN",
  "Lao PDR" ~ "LAO",
  "Malaysia" ~ "MYS",
  "Myanmar" ~ "MMR",
  "Philippines" ~ "PHL",
  "Singapore" ~ "SGP",
  "Thailand" ~ "THA",
  "Viet Nam" ~ "VNM"
)
any(is.na(meat$iso3))
nrow(unique(meat[, c("country", "iso3")]))
```

The `iso3` column maps each ASEAN country name to its three letter country code. The output from `any(is.na(meat$iso3))` confirms that there are no missing ISO3 mappings after the recoding step. The output from `nrow(unique(meat[, c("country", "iso3")]))` confirms that there are 10 unique country code pairs, matching the 10 ASEAN countries in the dataset.


# Consolidate the Results 

## AI Liaison Review

**Tool used:** Qwen3.6

**Useful suggestion:** The AI correctly suggested using `fct_collapse()` with named 
arguments to merge the four animal levels into `"red"` and `"white"`, which matched 
the permitted toolbox and worked without modification.

**Suboptimal response:** When asked to reveal column classes as a verifier cross-check 
(Section 3.1), the AI included `class(meat$iso3)` alongside the original four columns. 
This was incorrect because `iso3` does not exist at that point in the QMD — it is only 
created later in Section 3.5. Running the chunk in order would cause an error. The team 
identified the problem by tracing the QMD execution order and removed the `class(meat$iso3)` 
line from the Section 3.1 chunk.

**Overall, Qwen3.6 was a helpful collaborator for this lab. Most responses were correct
and toolbox-compliant, and the one suboptimal response was caught and corrected before
the final submission.**


## Reporter Review

As the Reporter, I reviewed the written explanations in the QMD to make sure the findings were clearly explained in plain language. I summarised the key results from the dataset inspection, missing value analysis, 2020 country comparison, factor construction, and ISO3 country code mapping.

The main findings are that the dataset contains 160 rows and 4 columns, covering 10 ASEAN countries, 4 animal categories, and 4 years from 2018 to 2021. The production column contains 4 missing values, all for Cambodia's mutton and goat production from 2018 to 2021. For the 2020 comparison, Indonesia had the highest poultry production, Thailand had the second highest poultry production, and 6 countries produced more poultry than pig.

I also checked that the written summaries matched the code outputs where possible and prepared the main points for the team's short presentation. The presentation should highlight the dataset structure, the concentrated missing values, the 2020 poultry findings, and one example of why AI generated code must be checked against the lab's permitted toolbox.


## Coder Review

TODO: Coder to complete this section after confirming the QMD renders successfully and code chunks run correctly.



## Constructive Critic Review

The Constructive Critic reviewed the QMD for clarity, structure, permitted toolbox compliance, and submission readiness.

First, the QMD was checked to ensure that the sections followed the lab tasks in order: inspecting the `meat` tibble, handling missing values, comparing countries in 2020, constructing factors, adding ISO3 country codes, and consolidating the results. The explanations were also reviewed to make sure they clearly described what the code does and why the output makes sense.

Second, the code chunks were scanned for functions and operators that are not allowed under the permitted toolbox. The final code uses permitted functions such as `read_csv()`, `class()`, `unique()`, `length()`, `nrow()`, `ncol()`, `glimpse()`, `head()`, `tail()`, `is.na()`, `any()`, `sum()`, `max()`, `min_rank()`, `desc()`, `identical()`, `factor()`, `levels()`, `fct_collapse()`, and `recode_values()`. No disallowed functions such as `filter()`, `select()`, `mutate()`, `summarise()`, or `case_when()` were found in the final code chunks.

The Constructive Critic also flagged final clean-up items before submission: the AI Liaison Review, Reporter Review, and Coder Review sections should be completed by the respective roles; every code chunk should have a unique label; the QMD should use the project-relative path `read_csv("meat.csv")`; and the QMD should be rendered to HTML successfully. The final ZIP archive should also be checked to ensure that it contains the QMD file, rendered HTML file, `meat.csv`, AI log, and any generated Quarto files.

## Navigator Review
I reviewed the QMD for overall coherence, flow, and alignment with the lab objectives. I also ensured that the QMD tells a clear story about the ASEAN meat production dataset, starting from basic inspection to handling missing values, comparing countries, constructing factors, adding ISO3 codes and also checked that the explanations are accessible to a general audience and that the key findings are highlighted effectively. Coordinated with the AI Liaison, Reporter, Coder, and Constructive Critic to ensure that all sections are completed and that the final submission meets the lab requirements.
